---
title: "DRRmodel"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Data Wrangling and Cleaning
Load in the required package
```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(rpart)
library(randomForest)
library(caret)
```

Load the data 
```{r}
data=read.csv("E:/DataArtist/THC/Cr/conversion_data.csv")
```

Check the basic information of data
```{r}
head(data)
str(data)
# observe the data carefully, observe the user base, benckmark it with the industry and market
summary(data)
```


## Visualization and EDA
Check the problemtic data
```{r}
# Check the outlier
sort(unique(data$age),decreasing = TRUE)
subset(data,data$age>79)
# remove the data
data=subset(data,data$age<79)

# Check the missing value using sapply function
sapply(data,function(x) sum(is.na(x)))

# Are there any duplicates in the data
# nrow(data)==length(unique(data$user_id))

# Join the table
# If the length is not eqivalent, when joining we should use left join

# data = merge(test,user, by = "user_id", all.x = TRUE)
```


EDA: Check the Distribution of Variables and The Relationship Between Dependent Variables
```{r}
# Example:Check the Relationship Between Country and Conversion Rate
library(dplyr)
data_country=data%>%group_by(country)%>%summarise(conversion_rate=mean(converted))
qplot(country,data=data_country,weight=conversion_rate,geom="bar")

# Example: Check the Relationship Between Total Pages Visited and Conversion Rate
data_pages=data%>%group_by(total_pages_visited)%>%summarise(conversion_rate=mean(converted))
qplot(total_pages_visited,conversion_rate,data=data_pages,geom="line")

# Example: Check the Relationship Between Age and Conversion Rate
data_ages=data%>%group_by(age)%>%summarise(conversion_rate=mean(converted))
qplot(age,conversion_rate,data=data_ages)
```
## Feature Engineering
Demonstrate how you will create new features based on the understanding of the business scenario
```{r}
#data = data.frame(data %>%
#group_by(ip_address) %>%
#mutate (ip_address_count = n())
#)

#data$purchase_time_wd = format(data$purchase_time, "%A" )
```

## Modeling or Statistical Analysis
Machine Learning and Predictive Modeling
```{r}
# Change all the categorical variables into factors
data$converted=as.factor(data$converted)
data$new_user=as.factor(data$new_user)
# Tricks: turn the level name into short names easy to plot
levels(data$country)[levels(data$country)=="Germany"]="DE"
```


Build up the model
```{r}
set.seed(3456)
trainIndex=sample(nrow(data),size=nrow(data)*0.66)
train_data=data[trainIndex,]
test_data=data[-trainIndex,]
# train and test split
rf=randomForest(y=train_data$converted,x=train_data[,-ncol(train_data)],y_test=test_data$converted,x_test=test_data[,-ncol(test_data)],ntree=100,mtry=3,keep.forest = TRUE)
rf
```
Build up a logistic regression model
```{r}
# training logistic regression model
logmodel <- glm(converted~., data = data, family = binomial)
cutoffs <- seq(0.1,0.9,0.1)
accuracy <- NULL
for (i in seq(along = cutoffs)){
    prediction <- ifelse(logmodel$fitted.values >= cutoffs[i], 1, 0) #Predicting for cut-off
accuracy <- c(accuracy,length(which(data$converted ==prediction))/length(prediction)*100)}

plot(cutoffs, accuracy, pch =19,type='b',col= "steelblue",
     main ="Logistic Regression", xlab="Cutoff Level", ylab = "Accuracy %")
```

```{r}
ctrl <- trainControl(method = "cv", number = 5, savePredictions = TRUE)
mod_fit <- train(converted~.,  data=data, method="glm", family="binomial",
                 trControl = ctrl,  tuneGrid=expand.grid(parameter=c(0.3, 0.4,0,5,0.6,0.7)))

mod_fit
```



Statistical Analysis
```{r}
# We can also conduct a t-test on the Chinese Customers between non-Chinese customers to see whether the conversion difference is statistically different

data.China = subset(data, country = "China")
data.NoneChina=subset(data, country != "China")
t.test(as.numeric(data.China$converted),as.numeric(data.NoneChina$converted))

```
The conversion rate in China is significantly lower than the conversion rate in Other Countries.


I will plot by country to see if the statistical difference is still existing, when controlled age 
```{r}
data_by_age = data %>%
group_by(age) %>%
summarize(china_vs_nonchina=mean(as.numeric(converted[country=="China"]))/mean(as.numeric(converted[country!="China"])))

qplot(age,china_vs_nonchina,data=data_by_age,geom="line")
```
From the plot, we can find that the above mentioned pattern still exists even when we controlled the age.

```{r}
# Further exploration: We can use decisoin tree to figure out if our randomization is successful.
```


## Model Validation(Feature Importance and Improve Prediction Accuracy)

If this problem is more about prediction accuracy, then spend more time on parameter tuning using cross validation techniques

If this problem is more about interpreability, then spend time on check the varianle importance

```{r}
# Rebuild a model without unactionable features, in this case total_pages_visited
rf2=randomForest(y=train_data$converted,x=train_data[,-c(5,ncol(train_data))],y_test=test_data$converted,x_test=test_data[,-ncol(test_data)],ntree=100,mtry=3,keep.forest = TRUE,classwt = c(0.7,0.3))
varImpPlot(rf2)
```
We can give some conslusion according to the plots such as new_user is the most important factor of the conversion rate and the source doesn't have a large weight. 


Further plot the partial dependence to provide more insights
```{r}
op=par(mfrow=c(2,2))
partialPlot(rf2, train_data, country, 1)
partialPlot(rf2, train_data, age, 1)
partialPlot(rf2, train_data, new_user, 1)
partialPlot(rf2, train_data, source, 1)
```
Partial dependence will help us to know the trend on the influence of independent variables on our cared KPI

In this case, we can draw some conclusions like:
+ Customer from China have a low conversion rate
+ Young user has a higher conversion rate


We can build a simple decision tree illustrate to the decision maker which are the most important segments and what are the most important features.
```{r}
tree = rpart(data$converted ~ ., data[, -c(5,ncol(data))],
control = rpart.control(maxdepth = 3),
parms = list(prior = c(0.7, 0.3))
)
tree
```
The pattern confirms our decision model.

## Actionable Insights and Conclusion
In this section, we should reconnect the math knowledge to the business. In this case we can draw the conclusion as follows: 
+ Young users have a high conversion rate and we should put more marketing force to reach out to young people.
+ The conversion rate of German is high, but the population of German customers is low, this is our potential market.
+ We should improve our sites on Chinese, the conversion rate of Chinese users is too low.
+ We should do some precision marketing strategy to tackle those users view a lot of pages and explore why the conversion rate suddenly fall when users are older than 30.
